The \dealii Library, Version 9.6

### 2024-08-19 9.6/paper.tex
vladimir was at clemson
Fix typo in post code

 \author[1*]{Pasquale~Claudio~Africa}
 \affil[1]{SISSA International School for Advanced Studies,
   mathLab,
   Via Bonomea, 265,
   34136O, Trieste, Italy.
   \texttt{pafrica@sissa.it}}

@@

\dealii version 9.6.0 was released X X, 2024.
This paper provides an
overview of the new features of this release and serves as a citable
reference for the \dealii software library version 9.6. \dealii is an
object-oriented finite element library used around the world in the
development of finite element solvers. It is available for free under the
GNU Lesser General Public License (LGPL). Downloads are available at
\url{https://www.dealii.org/} and \url{https://github.com/dealii/dealii}.

@@

The 9.6 release includes
\href{https://dealii.org/developer/doxygen/deal.II/changes_between_9_5_2_and_9_6_0.html}
     {around X incompatible changes};
see \cite{changes96}. Many of these
incompatibilities change internal
interfaces that are not usually used in external
applications. That said, the following are worth mentioning since they
may have been more widely used:
\begin{itemize}
  \item CUDAWrappers
\end{itemize}

@@

\dealii can interface with many other libraries:
\begin{multicols}{3}
  \begin{itemize}[leftmargin=4mm]
    \item ADOL-C \cite{griewank1996adolc}
    \item ArborX \cite{lebrun2020arborx}
    \item ARPACK \cite{lehoucq1998arpack}
    \item Assimp \cite{schulze2021assimp}
    \item BLAS and LAPACK \cite{anderson1999lapack}
    \item Boost \cite{boost-web-page}
    \item CGAL \cite{cgal-user-ref}
    \item cuSOLVER \cite{cusolver-web-page}
    \item cuSPARSE \cite{cusparse-web-page}
    \item Gmsh \cite{geuzaine2009gmsh}
    \item GSL \cite{galassi2009gsl,gsl-web-page}
    \item Ginkgo \cite{anzt2020ginkgo,anzt2022ginkgo}
    \item HDF5 \cite{hdf5-web-page}
    \item METIS \cite{karypis1998metis}
    \item MUMPS \cite{amestoy2001mumps,amestoy2019mumps}
    \item muparser \cite{muparser-web-page}
    \item OpenCASCADE \cite{opencascade-web-page}
    \item p4est \cite{burstedde2011p4est}
    \item PETSc \cite{petsc-user-ref,petsc-web-page}
    \item ROL \cite{ridzal2014rol}
    \item ScaLAPACK \cite{blackford1997scalapack}
    \item SLEPc \cite{hernandez2005slepc}
    \item SUNDIALS \cite{hindmarsh2005sundials}
    \item SymEngine \cite{symengine-web-page}
    \item TBB \cite{reinders2007tbb}
    \item Trilinos \cite{heroux2005trilinos,trilinos-web-page}
    \item UMFPACK \cite{davis2004umfpack}
  \end{itemize}
\end{multicols}
Please consider citing the appropriate references if you use
interfaces to these libraries.

@@

\dealii is a worldwide project with dozens of contributors around the
globe. Other than the authors of this paper, the following people
contributed code to this release:\\
%
% Uwe Koecher doesn't usually show up in the changelog, but
% we should make sure he's listed.
%

% This is up-to-date as of 2024-07-23 11:52PM CEST
\begin{quote}
Laryssa      Abdala,
Mathias      Anselmann,
Abbas        Ballout,
Maximilian   Bergbauer,
Julian       Brotz,
Marco        Feder,
Niklas       Fehn,
Menno        Fraters,
Quang        Hoang,
Vladimir     Ivannikov,
Tao          Jin,
Yimin        Jin,
Sebastian    Kinnewig,
Paras        Kumar,
Sébastien    Loriot,
Nils         Much,
Abdullah     Mujahid,
Bob          Myhill,
Paul A.      Patience,
Luz          Paz,
Laura        Prieto Saavedra,
Sebastian    Proell,
Hendrik      Ranocha,
Johannes     Resch,
Andreas      Ritthaler,
Malik        Scheifinger,
David        Schneider,
Magdalena    Schreter-Fleischhacker,
Richard      Schussnig,
Nils         Schween,
Kyle         Schwiebert,
Simranjeet   Singh,
Simon        Sticko,
Dominik      Still,
Jan Philipp  Thiele,
Thierry      Thomas,
Vinayak      Vijay,
Ivy          Weber,
Simon        Wiesheier,
Chengjiang   Yin,
Vladimir     Yushutin,
Stefano      Zampini.
\end{quote}
Their contributions are much appreciated!

@@

M.~Bergbauer was supported by the German Research Foundation (DFG) under the
project ``High-Performance Cut Discontinuous Galerkin Methods for Flow
Problems and Surface-Coupled Multiphysics Problems'' Grant Agreement
No.~456365667.

J.~Heinz was supported by the European Union’s Framework Programme for Research
and Innovation Horizon 2020 (2014-2020) under the Marie Sk\l{}odowska--Curie Grant
Agreement No. [812719].

T.~Heister was also partially supported by NSF
Awards OAC-2015848, DMS-2028346, and
EAR-1925575.

L.~Heltai and M~.Feder were partially supported by the Italian Ministry of
University and Research (MUR), under the grant MUR PRIN 2022 No. 2022WKWZA8
``Immersed methods for multiscale and multiphysics problems (IMMEDIATE)''.

@@

S. Zampini was supported by the KAUST Extreme Computing Research Center.

>>>>

 \author[1*]{Pasquale~Claudio~Africa}
 \affil[1]{SISSA International School for Advanced Studies,
   mathLab,
   Via Bonomea, 265,
   34136, Trieste, Italy.
   \texttt{pafrica@sissa.it}}

@@

\dealii version 9.6.0 was released August 11, 2024.
This paper provides an
overview of the new features of this release and serves as a citable
reference for the \dealii software library version 9.6. \dealii is an
object-oriented finite element library used around the world in the
development of finite element solvers. It is available for free under the
GNU Lesser General Public License (LGPL). Downloads are available at
\url{https://www.dealii.org/} and \url{https://github.com/dealii/dealii}.

@@

The 9.6 release includes
\href{https://dealii.org/developer/doxygen/deal.II/changes_between_9_5_2_and_9_6_0.html}
     {around X incompatible changes};
see \cite{changes96}. Many of these
incompatibilities change internal
interfaces that are not usually used in external
applications. That said, the following are worth mentioning since they
may have been more widely used:
\begin{itemize}
  \item CUDAWrappers, that enable the usage of cuSPARSE algorithms, have been deprecated and will be removed in the next release. Kokkos is now used for device-specific optimizations.
\end{itemize}

@@

\dealii can interface with many other libraries:
\begin{multicols}{3}
  \begin{itemize}[leftmargin=4mm]
    \item ADOL-C \cite{griewank1996adolc}
    \item ArborX \cite{lebrun2020arborx}
    \item ARPACK \cite{lehoucq1998arpack}
    \item Assimp \cite{schulze2021assimp}
    \item BLAS and LAPACK \cite{anderson1999lapack}
    \item Boost \cite{boost-web-page}
    \item CGAL \cite{cgal-user-ref}
    \item cuSOLVER \cite{cusolver-web-page}
    \item cuSPARSE \cite{cusparse-web-page}
    \item Gmsh \cite{geuzaine2009gmsh}
    \item GSL \cite{galassi2009gsl,gsl-web-page}
    \item Ginkgo \cite{anzt2020ginkgo,anzt2022ginkgo}
    \item HDF5 \cite{hdf5-web-page}
    \item METIS \cite{karypis1998metis}
    \item MUMPS \cite{amestoy2001mumps,amestoy2019mumps}
    \item muparser \cite{muparser-web-page}
    \item OpenCASCADE \cite{opencascade-web-page}
    \item p4est \cite{burstedde2011p4est}
    \item PETSc \cite{petsc-user-ref,petsc-web-page}
    \item ROL \cite{ridzal2014rol}
    \item ScaLAPACK \cite{blackford1997scalapack}
    \item SLEPc \cite{hernandez2005slepc}
    \item SUNDIALS \cite{hindmarsh2005sundials}
    \item SymEngine \cite{symengine-web-page}
    \item Taskflow \cite{huang2021taskflow}
    \item TBB \cite{reinders2007tbb}
    \item Trilinos \cite{heroux2005trilinos,trilinos-web-page}
    \item UMFPACK \cite{davis2004umfpack}
  \end{itemize}
\end{multicols}
Please consider citing the appropriate references if you use
interfaces to these libraries.

@@

\dealii is a worldwide project with dozens of contributors around the
globe. Other than the authors of this paper, the following people
contributed code to this release:\\

% This is up-to-date as of 2024-07-23 11:52PM CEST
\begin{quote}
Laryssa      Abdala,
Mathias      Anselmann,
Abbas        Ballout,
Maximilian   Bergbauer,
Julian       Brotz,
Marco        Feder,
Niklas       Fehn,
Menno        Fraters,
Quang        Hoang,
Vladimir     Ivannikov,
Tao          Jin,
Yimin        Jin,
Sebastian    Kinnewig,
Paras        Kumar,
Sébastien    Loriot,
Nils         Much,
Abdullah     Mujahid,
Bob          Myhill,
Paul A.      Patience,
Luz          Paz,
Laura        Prieto Saavedra,
Sebastian    Proell,
Hendrik      Ranocha,
Johannes     Resch,
Andreas      Ritthaler,
Malik        Scheifinger,
David        Schneider,
%Magdalena    Schreter-Fleischhacker,
Richard      Schussnig,
Nils         Schween,
Kyle         Schwiebert,
Simranjeet   Singh,
Simon        Sticko,
Dominik      Still,
%Jan Philipp  Thiele,
Thierry      Thomas,
Vinayak      Vijay,
Ivy          Weber,
Simon        Wiesheier,
Chengjiang   Yin,
%Vladimir     Yushutin,
Stefano      Zampini.
\end{quote}
Their contributions are much appreciated!

@@

T.~Heister and V.~Yushutin were also partiallty supported by NSF Awards OAC-2015848 and EAR-1925575.

T.~Heister was also partially supported by NSF OAC-2410848.

L.~Heltai was partially supported by the Italian Ministry of
University and Research (MUR), under the grant MUR PRIN 2022 No. 2022WKWZA8
``Immersed methods for multiscale and multiphysics problems (IMMEDIATE)''.

@@
